Visual proteomics using whole-lamella 2D template matching

### 2022-03-08 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/4e9e2eda33d911a965d898af77d32172b9a3ec9d.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/4e9e2eda33d911a965d898af77d32172b9a3ec9d/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1953050404

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/287b9950fc2bff7878d36aa1cbf2cb7f2082f798/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/287b9950fc2bff7878d36aa1cbf2cb7f2082f798}{jojoelfe/deco\_lace\_template\_matching\_manuscript@287b995}
on March 7, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/4e9e2eda33d911a965d898af77d32172b9a3ec9d/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/4e9e2eda33d911a965d898af77d32172b9a3ec9d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@4e9e2ed}
on March 8, 2022.
